MolProbity's Ultimate Rotamer-Library Distributions for Model Validation

### 2016-02-24 results.tex
Fixed rotamer count in results (we were way off due to intially including MSE) and cleared wording when explaining the two rotamer clusters we left out

\section{Results}
In the Top8000 system there are a total of 234 named rotamers which reach above the 0.3\% outlier cutoff and \textcolor{changecolor}{which passed manual examination of all examples within clusters that include $\le$ 8 datapoints (only two such clusters failed the test: both were Lys rotamers with $\le$ 4 datapoints)}. Many of the central values have shifted somewhat from the Top500 system, both because of much more and higher-quality data and also because of the new center-of-mass definition (see Section \ref{sec_md:chi_stats}), which we feel represents the clusters better than either the modal or the common-atom values defined previously \cite{lovell2000penultimate}. MolProbity's "ultimate" rotamers and their parameters are given in two tables: Table S3 describes the frequency and count of each rotamer in each residue type and Tables S4-S21 give central dihedral and covalent angle values for each rotamer. These numbers are available in CSV format on GitHub under \texttt{Top8000/Top8000\_rotamer\_central\_values} at \url{http://github.com/rlabduke/reference_data}. The more useful multi-dimensional distributions are also on GitHub, as linked in Section \ref{sec_md:contours}.

>>>>

\section{Results}
In the Top8000 system there are a total of 212 named rotamers which reach above the 0.3\% outlier cutoff and \textcolor{changecolor}{passed our manual examination. Clusters with $\le$ 8 datapoints were manually examined -- two Lys clusters lacked sufficient density to justify their inclusion}. Many of the central values have shifted somewhat from the Top500 system, both because of much more and higher-quality data and also because of the new center-of-mass definition (see Section \ref{sec_md:chi_stats}), which we feel represents the clusters better than either the modal or the common-atom values defined previously \cite{lovell2000penultimate}. MolProbity's "ultimate" rotamers and their parameters are given in two tables: Table S3 describes the frequency and count of each rotamer in each residue type and Tables S4-S21 give central dihedral and covalent angle values for each rotamer. These numbers are available in CSV format on GitHub under \texttt{Top8000/Top8000\_rotamer\_central\_values} at \url{http://github.com/rlabduke/reference_data}. The more useful multi-dimensional distributions are also on GitHub, as linked in Section \ref{sec_md:contours}.
